--- 
title       : "Regressions 3: Introduction to Matching Methods"
description : "This chapter will introduce you to using matching methods to find causal effects"
 
 
--- type:VideoExercise lang:r aspect_ratio:62.5 xp:50 skills:1 
## Matching Methods
*** =video_link
//player.vimeo.com/video/217555077

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 
## Reasons to Use Matching Methods. 
Megan the exercise freak (health coach) believes that eating out at restaurants can be good for people because it motivates them to exercise more the following day. She asks thousands of people whether they ate out at a restaurant the previous Saturday, and whether they spent any time exercising the following Sunday. She finds a positive correlation between eating at a restaurant and exercising the following day. Why might why might she want to use matching methods to assess whether there is a causal effect?

*** =instructions
- Because you didn't ask whether people why they chose to exercise on Sunday.
- Because most fitness clubs meet on Sundays.
- Because Sunday is most people's favorite day to exercise.
- Because people who eat out might have a higher propensity to exercise as well.

*** =sct
```{r}
msg1 = "Try again"
msg2 = "Try again"
msg3 = "Well done"
msg4 = "Try again"
test_mc(correct = 4, feedback_msgs = c(msg1,msg2,msg3,msg4))
```




--- type:VideoExercise lang:r aspect_ratio:62.5 xp:50 skills:1 
## The Lifetime Earnings of Veterans and Nonveterans
*** =video_link
//player.vimeo.com/video/217555250


--- type:MultipleChoiceExercise lang:r xp:50 skills:1 
## Why we Need Matching Methods
Why couldn't Angrist just compare the lifetime earnings of veterans and nonveterans with standard regression methods?
*** =instructions
- Because the people who applied to the military and got rejected are probably poor people in the first place.
- Because the military only rejects disabled people.
- Because the veterans who selected into the military may have had very different earnings trajectories than individuals who had not selected into the military.
- Because people who got rejected are likely to be disproportionately female.
*** =sct
```{r}
msg1 = "Correct!"
msg2 = "Try again"
msg3 = "Well done"
msg4 = "Try again"
test_mc(correct = 1, feedback_msgs = c(msg1,msg2,msg3,msg4))
```



--- type:VideoExercise lang:r aspect_ratio:62.5 xp:50 skills:1 
## The Unconfoundedness Assumption in Angrist's Study on the Effect of Veteran Status on Lifetime Earnings
*** =video_link
//player.vimeo.com/video/217555486



--- type:MultipleChoiceExercise lang:r xp:50 skills:1 
## Replication and Validity
Suppose you replicate the Angrist analysis using more recent data from 1992-2015, and find approximately zero causal effects for both whites and nonwhites, for all stages of life. On its own, would this finding invalidate Angrist's analysis?
*** =instructions
- Yes
- No
*** =sct
```{r}
msg1 = "Try again"
msg2 = "Correct! This is a relatively difficult question. It is possible that unit level causal effects change over time, so using a different data set with more recent data may simply tell us that the causal effect has been decreasing over time. If this is the case, your replication does not necessarily invalidate his analysis. On the other hand, if you have a strong reason to believe that the causal effects do not change over time, then this would perhaps call into question the validity of the earlier findings."
test_mc(correct = 2, feedback_msgs = c(msg1,msg2))
```

--- type:MultipleChoiceExercise lang:r xp:50 skills:1 
## Causal Inference with Matching Methods 
Suppose you want to know the effect of enrollment in a Massive Open Online Course (MOOC) on income. You are worried that people with more traditional education-e.g., someone with a bachelor's degree-will be more likely to enroll in a MOOC and also more likely to make more income, compared to someone with less traditional education-e.g., someone with only a high school diploma. So you make the unconfoundedness assumption that, holding traditional education fixed, people randomly enroll in MOOCs. You then use matching to estimate the ATE of MOOC enrollment, and find that it is positive. What policy might you recommend from this, if any?

*** =instructions
- No recommendation-correlation does not equal causation and so we cannot conclude what the effect of MOOC enrollment is.
- MOOC enrollment should be promoted as a means of improving people's wages.
- The costs of enrolling in MOOCs should qualify for federal student loans, just as traditional educational approaches do.
- MOOCs should be banned so as to promote traditional educational methods.

*** =sct
```{r}
msg1 = "Assuming you believe the unconfoundedness assumption, the matching method does actually get a true causal effect. As usual, there is always room for debate on whether this assumption is credible, but this answer overstates that case."
msg2 = "Correct! Since the effect of MOOCs on income is positive, policies which promote MOOCs will tend to increase income on average."
msg3 = "Our evidence suggests that MOOCs may help individuals achieve better incomes, but we do not have enough informtion to justify whether MOOCs should qualify for student loans. For example, given that MOOCs are relatively inexpensive to enroll in, it may be unnecessary or unreasonably costly to create a system that provides federal student loans for MOOCs."
msg4 = "Since the study finds a positive treatment effect of MOOCs on income, this is an unintuitive conclusion to arrive at."
test_mc(correct = 2, feedback_msgs = c(msg1,msg2,msg3,msg4))
```



--- type:VideoExercise lang:r aspect_ratio:62.5 xp:50 skills:1 
## The Effect of Volunteer Military Service on Lifetime Earnings
*** =video_link
//player.vimeo.com/video/217555588


--- type:NormalExercise lang:r aspect_ratio:62.5 xp:50 skills:1
## Propensity Score Matching in R
A recent study examined how playing the multiplayer online battle arena video game, Neo Elite Raging Denizens (NERD), effects people's communication skills. Despite their coarse language in the game, a detailed psychological survey indicated that NERD players have no different language skills than average. This finding held even when the researchers used OLS regression and controlled for various factors that are related to language skills. However, the sample was highly unbalanced, such that matching techniques may be required. With the dataset, `NERD`, use matching techniques to better estimate the average treatment effect of playing NERD.

*** =instructions
- Do something

*** =pre_exercise_code
```{r}
#Original dataset
library(MatchIt)
set.seed(7)
n=8008
#Create rnorm function that allows for min and max
    rtnorm <- function(n, mean, sd, min = -Inf, max = Inf){
      qnorm(runif(n, pnorm(min, mean, sd), pnorm(max, mean, sd)), mean, sd)
    }
#Create rounding function that allows to round to numbers above 1
    mround <- function(x,base){ 
      base*round(x/base) 
    } 
#Creat dataset
    NERD<-data.frame(ParentEducation=round(rtnorm(n,15,sd=3,min=10,max=20),1),
                     BooksOwned=round(rtnorm(n,60,sd=15,min=35,max=100),1),
                     ReadsBlogs=rbinom(n,1,.25),
                     Siblings=rbinom(n,1,.7),
                     Bilingual=rbinom(n,1,.1),
                     LikesBooks=rbinom(n,1,.3)
    )
    NERD$Treatment<-NERD$ParentEducation+NERD$BooksOwned/4+NERD$ReadsBlogs*10-NERD$Siblings*5+NERD$LikesBooks*10 +rnorm(n,10,3)
    NERD$Treatment<-NERD$Treatment/max(NERD$Treatment)
    NERD$Treatment<-ifelse(NERD$ParentEducation<17 | NERD$BooksOwned<70,0,NERD$Treatment)
    NERD$Treatment<-NERD$Treatment
    NERD$Treatment<-rbinom(n,1,NERD$Treatment)
    NERD$Communication<-2.5*NERD$Treatment+NERD$ParentEducation^1.4+-.01*NERD$Treatment*NERD$ParentEducation+-.01*NERD$Treatment*NERD$BooksOwned^1.2+NERD$BooksOwned*.6+1.5*NERD$ReadsBlogs+NERD$LikesBooks*.7 + NERD$Siblings + .25*NERD$Bilingual +rnorm(n,5,1) 
    NERD$Communication<-round(NERD$Communication/max(NERD$Communication)*10)

```
*** =sample_code
```{r}
# As usual, let's first look at the variables in the dataset. The dependent variable in our model, Communication, was measured via a battery of questions and put on a 1:10 scale, with 1=very poor communication skills and 10=very good communication skills. Whether the respondent plays NERD is measured via the Treatment variable. Only a small proportion of our sample actually played NERD. The other variables in the dataset are  factors that could possibly affect a person's communication ability. Most are measured as binary or "dummy" variables. For example, respondents who had any siblings were marked with a "1" in the siblings variable. 
    summary(NERD)

# Let's first estimate a model for Communication skills based on every other variable in the dataset. Use R's glm() formula. 

#-------------------- Question 1 --------------------#
      Solution1<-glm()
#----------------------------------------------------#

# Is the effect of "Treatment" in Solution1 positive and statistically significant? Use the summary command on Solution1 to check. Answer with "Yes" or "No"
    
#-------------------- Question 2 --------------------#
      Solution2<-""
#----------------------------------------------------#
    
# Matching methods are most useful when the treatment group is likely to be different from the general population. To determine if the treatment group differs from the population on any variable, we could run a t.test. The following is an example of how we would test if the treatment group tends to have more or less educated parents than the rest of the sample. This t.test suggests that our Treatment group has much more educated parents than in our control group.
    t.test(NERD$ParentEducation[NERD$Treatment==1],NERD$ParentEducation[NERD$Treatment==0])

# Regression models aren't perfect at measuring causal effects in unbalanced data. A more robust way to test the effect of our treatment on communication skills is through matching methods. Matching methods balance the treatment group with the control group so that they are more identical. In R, the best tool for doing matching is the "MatchIt" package. Below, we use the MatchIt package to subset our NERD dataset so that our control group contains observations that are most similar to those in our treatment group. The below syntax builds a model for estimating "Treatment" by all other control variables in our dataset, and subsets the NERD dataset to observations that have a high predicted probability for being in the treatment group. There are many methods for matching data, but in this question, we use MatchIt's default methods. 
    match.it <- matchit(Treatment ~ ParentEducation+BooksOwned+ReadsBlogs+Siblings+Bilingual+LikesBooks, data = NERD)
    matched.NERD <- match.data(match.it)[1:ncol(NERD)]
    
# To compare the matched dataset to the orginal dataset, we use the summary command on the object produced by the "matchit" formula. The "Summary of balance for all data" shows mean values of each variable across our original treatment and control groups, and the "Summary of balance for matched data" shows mean values of each variable across our matched dataset. You may notice that the mean values between the treatment and control groups are much more similar in the matched dataset than in the original dataset. The "Sample sizes" output shows that the algorithm matched one observation in the control group for each observation in the treatment group.
    summary(match.it)    
    
# Let's now estimate a regression model for communication skills using our matched dataset (matched.NERD). The syntax should be identical to Solution1, except that we are using the matched.NERD dataset.
    
#-------------------- Question 3 --------------------#
      Solution3<-glm()
#----------------------------------------------------#

# Is the effect of "Treatment" in Solution3 positive and statistically significant? Use the summary command on Solution3 to check. Answer with "Yes" or "No"
    
#-------------------- Question 4 --------------------#
      Solution4<-""
#----------------------------------------------------#

```
*** =solution
```{r}
   Solution1<-glm(Communication~ ParentEducation+BooksOwned+ReadsBlogs+Siblings+Bilingual+LikesBooks+Treatment,data=NERD)
   Solution2<-"Yes"
   Solution3<-glm(Communication~ ParentEducation+BooksOwned+ReadsBlogs+Siblings+Bilingual+LikesBooks+Treatment,data=matched.NERD)
   Solution4<-"No"
```
*** =sct
```{r}
test_object("Solution2")
test_object("Solution4")
success_msg("Good work! There orignally appeared to be a positive and statistically significant effect for playing NERD on respondent's communication skills, but when we balanced the data, this effect disappeared. This suggests that playing NERD does not improve people's communication skills; rather, NERD players tend to have good communication skills for a variety of other reasons.")
```



--- type:VideoExercise lang:r aspect_ratio:62.5 xp:50 skills:1 
## The Credibility of the Unconfoundedness Assumption
*** =video_link
//player.vimeo.com/video/217555887


--- type:MultipleChoiceExercise lang:r xp:50 skills:1 
## Assumptions and Causality
Since all regression models rely on the unconfoundedness assumption, can they ever support claims about causality?

*** =instructions
- Yes
- No
*** =sct
```{r}
msg1 = "Correct! All scientific theories and models are based on our assumptions about the world. Few, if any, statistical models can prove whether two variables are causally related. However, if our models rest on reasonable assumptions, they can support our claims about causality. This is also why we have so many models to test causal relationships. There are many statistical models where the unconfoundedness assumption is more plausible than in OLS regression"
msg2 = "Try again"
test_mc(correct = 1, feedback_msgs = c(msg1,msg2))
```
